### 2018-03-06 Physics Notes/Nuclear Physics/Radioactivity/Radioactivity.tex
Physics Radioactivity notes update

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}
\usepackage{tabularx}
\usetikzlibrary{decorations, decorations.text,positioning,quotes,arrows.meta,decorations.markings,3d,shapes,decorations.pathmorphing}
\pgfplotsset{width=10cm,compat=1.9}
\usepackage[super]{nth}
\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}
\hyphenpenalty =10000
\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Physics - Nuclear Physics}
\rfoot{Page \thepage}
\usepackage{mathtools}
\usetikzlibrary{calc,quotes,angles}
\tikzstyle{arrow} = [thick,->,>=stealth]
\begin{document}
\begin{center}
\underline{\huge Radioactivity}
\end{center}
\section{Rutherford Scattering}
\subsection{The plum pudding model}
\includegraphics[width=3cm] {plum.jpg}  
\includegraphics[width=3cm] {Plumpudding.png}
\\
The plum pudding model was the initial model of the atom, stating a sphere of positive charge with electrons embedded into it.
\subsection{Rutherford's experiment}
\includegraphics[width=6cm] {scatter.png}\\
Rutherford's experiment involved firing a beam of alpha particles at gold foil and measuring the paths of particles from the foil.
\begin{itemize}
\item Gold was used as it was expected to have a large nucleus
\item The screen fluoresces when collided with
\item This showed the atom was mostly empty space with a positive nucleus
\end{itemize}
\subsubsection{Results}

@@

>>>>

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}
\usepackage{tabularx}
\usepackage{relsize}
\usetikzlibrary{decorations, decorations.text,positioning,quotes,arrows.meta,decorations.markings,3d,shapes,decorations.pathmorphing}
\pgfplotsset{width=10cm,compat=1.9}
\usepackage[super]{nth}
\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}
\hyphenpenalty =10000
\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Physics - Nuclear Physics}
\rfoot{Page \thepage}
\usepackage{mathtools}
\usetikzlibrary{calc,quotes,angles}
\tikzstyle{arrow} = [thick,->,>=stealth]
\begin{document}
\begin{center}
\underline{\huge Radioactivity}
\end{center}
\section{Rutherford Scattering}
\subsection{The plum pudding model}
\includegraphics[width=3cm] {plum.jpg}  
\includegraphics[width=3cm] {Plumpudding.png}
\\
The plum pudding model was the initial model of the atom, stating a sphere of positive charge with electrons embedded into it.
\subsection{Rutherford's experiment}
\includegraphics[width=6cm] {scatter.png}\\
Rutherford's experiment involved firing a beam of alpha particles at gold foil and measuring the paths of particles from the foil.
\begin{itemize}
\item Gold was used as it was expected to have a large nucleus
\item The screen fluoresces when collided with
\item This showed the atom was mostly empty space with a positive nucleus
\end{itemize}
\subsubsection{Results}

@@

\section{Nuclear radius}
\subsection{High energy electron diffraction}
When a beam of high energy electrons is directed at a thin solid sample of an element they are diffracted by the nuclei of the atoms.\\
The electrons are diffracted by the nuclei because of their de Broglie wavelength, this is approximately equal to the radius of the nuclei. The detector measures the number of electrons per second at different angles.\\
The scattering of the beam of electrons occurs due to the charge, this causes intensity to decrease as angle increases.\\
The minimum on the graph can then be used to find the radius of the nucleus.
\subsection{Dependence of nuclear radius on nucleon number}
It can be shown that radius depends on mass according to:
$$\mathlarger{R=r_0A^{\frac{1}{3}}}$$
Where $r_0$ is the constant 1.05fm\\
The graph of $\ln(R)$ against $\ln(A)$ gives a line with gradient $\frac{1}{3}$ and y intercept equal to $\ln(r_0)$\\
The graph of R against $A^{\frac{1}{3}}$ gives a straight line through the origin with gradient $r_0$\\
$$V=\frac{4}{3}\pi R^3=\frac{4}{3}\pi(r_0A^{\frac{1}{3}})^3=\frac{4}{3}\pi r_0^3A$$
As $\textrm{Density}=\frac{\textrm{Mass}}{\textrm{Volume}}$
$$\textrm{Density}=\frac{Au}{\frac{4}{3}\pi r_0^3A}=\frac{1u}{4\pi r_0^3}=\frac{1.661\times10^{-27}}{\frac{4}{3}\pi(1.05\times10^{-15})^3}=3.4\times10^{17}kgm^{-3}$$
